\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage[hidelinks]{hyperref}

\title{Teoremas Básicos hacia una Demostración Completa de RH}
\author{José Manuel Mota Burruezo}
\date{\today}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{cor}[theorem]{Corollary}

\begin{document}
\maketitle
\tableofcontents

\input{rigidez_arquimediana.tex}
\input{unicidad_paley_wiener.tex}
\input{de_branges.tex}
\input{axiomas_a_lemas.tex}
\input{factor_arquimediano.tex}
\input{localizacion_ceros.tex}

\section*{Referencias}
\begin{thebibliography}{20}
\bibitem{Tate1967}
J. Tate, \emph{Fourier Analysis in Number Fields and Hecke's Zeta-Functions}, 
in Algebraic Number Theory, ed. J. W. S. Cassels and A. Fröhlich, Academic Press, 1967, pp. 305--347.

\bibitem{Weil1964}
A. Weil, \emph{Sur certains groupes d'opérateurs unitaires}, Acta Math. 111 (1964), 143--211.

\bibitem{BirmanSolomyak2003}
M. Sh. Birman and M. Z. Solomyak, \emph{Double Operator Integrals in a Hilbert Space}, 
Integr. Equ. Oper. Theory 47 (2003), 131--168. DOI: 10.1007/s00020-003-1137-8.

\bibitem{deBranges1986}
L. de Branges, \emph{Hilbert Spaces of Entire Functions}, Prentice-Hall, 1968.

\bibitem{PaleyWiener1934}
R. E. A. C. Paley and N. Wiener, \emph{Fourier Transforms in the Complex Domain}, 
American Mathematical Society Colloquium Publications, Vol. 19, AMS, 1934.

\bibitem{Hamburger1921}
H. Hamburger, \emph{Über eine Erweiterung des Stieltjesschen Momentenproblems}, 
Math. Ann. 81 (1921), 235--319.

\bibitem{Simon2005}
B. Simon, \emph{Trace Ideals and Their Applications}, 2nd ed., AMS, 2005, 
Thms. 9.2-9.3. DOI: 10.1090/surv/017.

\bibitem{IK2004}
H. Iwaniec and E. Kowalski, \emph{Analytic Number Theory}, Amer. Math. Soc., 2004.

\bibitem{Guinand1955}
A. P. Guinand, \emph{A summation formula in the theory of prime numbers}, 
Proc. London Math. Soc. (2) 50 (1955), 107--119.
\end{thebibliography}

\end{document}
