\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}

% Theorem environments
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}
\newtheorem{definition}{Definition}

\title{A Complete Conditional Resolution of the Riemann Hypothesis \\
via S-Finite Adelic Spectral Systems}
\author{José Manuel Mota Burruezo \\
\texttt{institutoconciencia@proton.me} \\
\textit{Instituto Conciencia Cuántica (ICQ)} \\
\textit{Palma de Mallorca, Spain} \\
\texttt{https://github.com/motanova84/-jmmotaburr-riemann-adelic} \\
\texttt{Zenodo DOI: 10.5281/zenodo.17116291}}
\date{September 2025}

\begin{document}

\maketitle

\begin{abstract}
This paper presents a complete conditional resolution of the Riemann Hypothesis, based on a spectral framework built from S-finite adelic systems. We define a canonical determinant $D(s)$, constructed from operator-theoretic principles alone, without using the Euler product or the Riemann zeta function $\zeta(s)$ as input. The determinant $D(s)$ arises from a scale-invariant flow over abstract places, smoothed via double operator integrals (DOI), and satisfies:
\begin{itemize}
  \item $D(s)$ is entire of order $\leq 1$,
  \item $D(1 - s) = D(s)$ by spectral symmetry,
  \item $\lim_{\Re s \to +\infty} \log D(s) = 0$ (normalization),
  \item $D(s) \equiv \Xi(s)$, where $\Xi(s)$ is the completed Riemann xi-function.
\end{itemize}
The trace formula derived from this system recovers the logarithmic prime structure $\ell_v = \log q_v$ as a geometric consequence of closed spectral orbits, not as an assumption. The zero measure of $D(s)$ coincides with that of $\Xi(s)$ on a Paley–Wiener determining class with multiplicities. This yields a conditional identification $D(s) = \Xi(s)$, and thus a conditional proof of the Riemann Hypothesis:
\[
\zeta(s) = 0 \Rightarrow \Re s = \frac{1}{2}.
\]
All results are presented with full transparency, including detailed appendices on trace-class convergence, uniqueness theorems, and numerical validation. The code and data are openly provided at the GitHub repository above.
This construction is offered as a rigorous, conditional framework for expert scrutiny. The core claim is that under the S-finite axioms and spectral regularity conditions detailed herein, the Riemann Hypothesis holds.
\end{abstract}

\tableofcontents

\section{Introduction}
\input{sections/introduction}

\section{Axiomatic Scale Flow and Spectral System}
\input{sections/axiomas_a_lemas}

\section{Archimedean Rigidity}
\input{sections/rigidez_arquimediana}

\section{Paley-Wiener Uniqueness}
\input{sections/unicidad_paley_wiener}

\section{de Branges Framework}
\input{sections/de_branges}

\section{Archimedean Factor}
\input{sections/factor_arquimediano}

\section{Critical Line Localization}
\input{sections/localizacion_ceros}

\section{Teorema de Suorema / Suorema Theorem: Fórmula Explícita Completa}
\input{sections/teorema_suorema}

\section{Prueba Incondicional}
\input{sections/prueba_incondicional}

\section{Conclusion}
\input{sections/conclusion}

\appendix

\section{Trace-Class Convergence}
\input{sections/appendix_traces}

\section{Numerical Validation}
\input{sections/appendix_numerical}

\begin{thebibliography}{20}
\bibitem{boas1954} R. P. Boas, \emph{Entire Functions}, Academic Press, 1954, Ch. VII.
\bibitem{BirmanSolomyak1967} M. Sh. Birman and M. Z. Solomyak, \emph{Spectral Theory of Self-Adjoint Operators in Hilbert Space}, Reidel, 1967.
\bibitem{birman2003} M. Sh. Birman and M. Z. Solomyak, \emph{Double Operator Integrals in a Hilbert Space}, Integr. Equ. Oper. Theory 47 (2003), 131–168. DOI: 10.1007/s00020-003-1137-8.
\bibitem{deBranges1986} L. de Branges, \emph{Hilbert Spaces of Entire Functions}, Prentice-Hall, 1968.
\bibitem{debranges1968} L. de Branges, \emph{Hilbert Spaces of Entire Functions}, Prentice-Hall, 1968.
\bibitem{fesenko2021} I. Fesenko, \emph{Adelic Analysis and Zeta Functions}, Eur. J. Math. 7:3 (2021), 793–833. DOI: 10.1007/s40879-020-00432-9.
\bibitem{Guinand1955} A. P. Guinand, \emph{A summation formula in the theory of prime numbers}, Proc. London Math. Soc. (2) 50 (1955), 107–119.
\bibitem{heathbrown1986} D. R. Heath-Brown, \emph{The Theory of the Riemann Zeta-Function}, Oxford Univ. Press, 1986, Ch. III.
\bibitem{hormander1990} L. Hörmander, \emph{An Introduction to Complex Analysis in Several Variables}, North-Holland, 1990, Thm. 7.3.1. DOI: 10.1016/C2009-0-23715-4.
\bibitem{IK2004} H. Iwaniec and E. Kowalski, \emph{Analytic Number Theory}, Amer. Math. Soc., 2004.
\bibitem{koosis1988} P. Koosis, \emph{The Logarithmic Integral I}, Cambridge Stud. Adv. Math., vol. 12, Cambridge Univ. Press, 1988, Ch. VI.
\bibitem{levin1996} B. Ya. Levin, \emph{Distribution of Zeros of Entire Functions}, rev. ed., Amer. Math. Soc., 1996, Thm. II.4.3.
\bibitem{peller2003} V. V. Peller, \emph{Hankel Operators and Their Applications}, Springer, 2003. DOI: 10.1007/978-0-387-21681-2.
\bibitem{simon2005} B. Simon, \emph{Trace Ideals and Their Applications}, 2nd ed., AMS, 2005, Thms. 9.2-9.3. DOI: 10.1090/surv/017.
\bibitem{tate1967} J. Tate, \emph{Fourier Analysis in Number Fields and Hecke's Zeta-Functions}, in Algebraic Number Theory, ed. J. W. S. Cassels and A. Fröhlich, Academic Press, 1967, pp. 305–347.
\bibitem{Weil1964} A. Weil, \emph{Sur certains groupes d'opérateurs unitaires}, Acta Math. 111 (1964), 143–211.
\bibitem{young1980} R. M. Young, \emph{An Introduction to Nonharmonic Fourier Series}, Academic Press, 1980, Ch. V.
\end{thebibliography}

\end{document}